Binary Latent Representations for Efficient Ranking

### 2017-08-14 paper/paper.tex
Add an alternatives section.

>>>>

\section{Alternative approaches}
Given the limited success of binary embedding, a more promising approach is offered by existing work that focuses on reducing the number of dot products which need to be performed in order to retrieve top recommendations. \citet{koenigstein2012efficient} introduces an exact branch-and-bound based on metric trees as well as an approximate algorithm that clusters users and serves recommendations computed for the cluster centers. \citet{shrivastava2014asymmetric} extend well-known \citep{indyk1998approximate} locality-sensitive hashing techniques to maximum inner product search (MIPS) through asymmetric transformations of the query and candidate vectors.

The method that is most closely related to the model we present in this paper is \citet{Shen_2015_ICCV}, who expand on MIPS by learning asymmetric binary hash functions. The hash functions are trained to minimize the L2 norm between the inner product matrix of the original input vectors and the inner product matrix of their binary representations.
